\begin{abstract}
Online programming discussion platforms such as Stack Overflow have a rich source of ready to use code snippets for software developers. 
It is the de fac-to place where developers go to find solutions. %from the coding snippets given as answers to posted problems by the online developer community. 
However, previous research work has shown that developers have a tendency to directly copy-paste insecure code snippets from 
Stack Overflow into their production level code. 
As a result without any countermeasures Stack Overflow is becoming one of major sources of causing vulnerabilities in production level source code. 
To address this problem, in this project, we tackle the problem of analyzing code snippets found on Stack overflow. 
This is challenging since code snippets from Stack overflow are often-times erroneous, incomplete, and lack dependencies which makes 
it harder to analyze them by state-of-the-art static tools.
In this paper we identify 8 common insecure patterns by analyzing a collection of 1.6K code snippets from Stack Overflow. 
We use a combination of keyword searching and backward flow analysis to detect these 8 common insecure patterns. 
We believe that by identifying the common insecure patterns in code snippets, found online programming discussion platforms websites such as Stack Overflow,  
it is possible to encourage developers to write secure code snippets, and discourage them from copy-pasting insecure code snippets
into production level source code.
\end{abstract}